---
title: "Kickstarter"
author: "Abhijit Haridas"
date: "12/05/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Importing Necessary Libraries



```{r import libraries, echo = FALSE}

# install.packages("devtools")
# require(devtools)
# install.packages("irlba")
# install_version("text2vec", version = "0.5.1", repos = "http://cran.us.r-project.org")
# install.packages("tm")
# install.packages("SnowballC")
# install.packages("vip")

library(text2vec)


library(splitstackshape)
library(tidyverse)
library(dplyr)
library(tree)
library(ggplot2)
library(glmnet)
library(e1071)
library(randomForest)
library(gbm)
library(tm)
library(SnowballC)
library(glmnet)
library(vip)
library(xgboost)
library(naivebayes)
library(tidyr)
library(fastDummies)
library(lightgbm)

memory.limit(10240)

```

## Import Kickstarter Data

This Section imports kickstarter dataset.

```{r import dataset, echo = FALSE, warnings=FALSE}

trainxs <- read.csv("ks_training_X.csv")
trainys <- read.csv('ks_training_y.csv')
testxs <- read.csv('ks_test_X.csv')
income_per_capita<-read.csv("pcap_us.csv")
income_per_capita<-rename(income_per_capita,"State" = "ï..State")

view(income_per_capita)
trains <- trainxs %>%
  left_join(trainys, by = "id") %>%
  mutate(success = as.factor(success),
         big_hit = as.factor(big_hit))


cleans <- trains%>%
  mutate(
    # location_type = as.factor(location_type),
    region = as.factor(region),
    # category_parent = as.factor(category_parent),
    # color_foreground = as.factor(color_foreground),
    # color_background = as.factor(color_background),
    # accent_color = as.factor(accent_color),
    # captions = as.factor(captions),
    deadline = as.Date(deadline)
  )

### Category wise Average Goal
cleans<-cleans%>%
  group_by(category_parent) %>% mutate(average_goal_by_cat_parent = mean(goal)) %>%ungroup()

### Creator Name

cleans <- cleans %>%
  group_by(creator_name) %>%
  mutate(count = n()) %>%
  ungroup() %>%
  mutate(quantile_rank = ntile(count, 4),
         top_creator_quartile = as.factor(ifelse(quantile_rank == 1, "YES", "NO")))


#### Top 10 Creator Names by number of projects
##### Sort original dataframe by descending order of number of projects
cleans_sorted <- cleans %>%
  group_by(creator_name) %>%
  mutate(count_creator_name = n()) %>%
  arrange(desc(count_creator_name))

##### Get names of creators of this dataframe
top_10_creator_name_filter<-unique(cleans_sorted$creator_name)

##### Remove the initally created sorted dataframe
rm(cleans_sorted)

##### Filter just top 10 names and store them in a vector
top_10_creator_name_filter = c(head(top_10_creator_name_filter, n=10))

##### Mutate original data with inclusive exclusive of top 10 filter
cleans<-cleans%>%mutate(top10_creators_by_num_projects = ifelse(creator_name%in%top_10_creator_name_filter,"YES","NO"),
                        top10_creators_by_num_projects = as.factor(top10_creators_by_num_projects))


#### Top 10 Creator Names by average goal

average_goal_by_creator <- cleans %>%group_by(creator_name)%>%
  mutate (average_goal = mean(goal))%>%arrange(desc(average_goal))

##### Get names of creators of this dataframe
top_10_creator_name_filter<-unique(average_goal_by_creator$creator_name)

##### Remove the initally created sorted dataframe
rm(average_goal_by_creator)

##### Filter just top 10 names and store them in a vector
top_10_creator_name_filter = c(head(top_10_creator_name_filter, n=10))

##### Mutate original data with inclusive exclusive of top 10 filter
cleans<-cleans%>%mutate(top10_creators_by_average_goal = ifelse(creator_name%in%top_10_creator_name_filter,"YES","NO"),
                        top10_creators_by_average_goal=as.factor(top10_creators_by_average_goal))



### 2. Duration between created and launched at and Duration between launched at and deadline 
cleans <- cleans %>%
  mutate(created_at = as.Date(created_at),
         launched_at = as.Date(launched_at),
         target_duration = launched_at - created_at,
         funding_duration = deadline - launched_at)

###3. Location Slug:- Separate Name and City
cleans <- cleans %>%
  separate(location_slug, c("City", "State"), sep = -3) %>%
  mutate( City = as.character(gsub("-"," ", City)),
    State = as.character(gsub("-","",State)),
    State = as.factor(State),
    City = as.factor(City))


cleans <- cleans %>%
  left_join(income_per_capita, by = "State")

###4. Location Type:- Group less frequently occuring location types

cleans<-cleans%>%group_by(location_type)%>%mutate(count_location_type = n())%>%ungroup()%>% mutate(location_type = ifelse(count_location_type<500,"Other",location_type),
                                                                                                   location_type = as.factor(location_type),
                                                                                                   region = as.factor(region),
                                                                                                   category_name = as.factor(category_name))

###5. Category within Category Parent - Find if category is top in the parent or not
category_name_sorted<-cleans%>%group_by(category_parent,category_name)%>%mutate(count_category_name = n())%>%arrange(desc(count_category_name))


##### Get names of category of this dataframe
top_10_category_name_filter<-unique(category_name_sorted$category_name)


##### Remove the initally created sorted dataframe
rm(category_name_sorted)

##### Filter just top 10 names and store them in a vector
top_10_category_name_filter = c(head(top_10_category_name_filter, n=10))

##### Mutate original data with inclusive exclusive of top 10 filter
cleans<-cleans%>%mutate(category_in_top_10 = ifelse(category_name%in%top_10_category_name_filter,"YES","NO"),
                        category_in_top_10 = as.factor(category_in_top_10))

###5. Female Creator> Male Creator? and Female Project>Male Project?
cleans<-cleans%>%mutate(fem_creators_greater_than_male_creators = ifelse(female_creator>male_creator,"YES","NO"),
                        fem_creators_greater_than_male_creators = as.factor(fem_creators_greater_than_male_creators))

cleans<-cleans%>%mutate(fem_projects_greater_than_male_projects = ifelse(female_project>male_project,"YES","NO"),
                        fem_projects_greater_than_male_projects=as.factor(fem_projects_greater_than_male_projects))


###6. Replace all NAs in (isTextPic,...) with "Missing"
# vectoreplace<-c("isbwImg1","isShapePic","isDiagramPic","isCalendarPic","isLogoPic","isTextPic","captions","color_foreground","color_background","accent_color")

cleans$isbwImg1[is.na(cleans$isbwImg1)]<-"Missing"
cleans$isShapePic[is.na(cleans$isShapePic)]<-"Missing"
cleans$isDiagramPic[is.na(cleans$isDiagramPic)]<-"Missing"
cleans$isCalendarPic[is.na(cleans$isCalendarPic)]<-"Missing"
cleans$isTextPic[is.na(cleans$isTextPic)]<-"Missing"
cleans$isLogoPic[is.na(cleans$isLogoPic)]<-"Missing"
cleans$captions[is.na(cleans$captions)]<-"Missing"
cleans$color_foreground[is.na(cleans$color_foreground)]<-"Missing"
cleans$color_background[is.na(cleans$color_background)]<-"Missing"
cleans$accent_color[is.na(cleans$accent_color)]<-"Missing"

###7. Create Dummy Variables for Tag Names

# cleans<-cSplit_e(cleans, "tag_names", "|", type = "character", fill = 0, drop = T)

# Problem Encountered: Too Many Tags leading to too many columns - Cannot allocate it in a dataframe

###8. affin_positive and affin_negative

cleans<-cleans%>%mutate(afinn_diff = afinn_pos - afinn_neg)

cleans<-cleans%>%mutate(afinn_positive_higher = ifelse(afinn_pos>afinn_neg,"YES","NO"),
                        afinn_positive_higher = as.factor(afinn_positive_higher))


###9. Binning Goal Variable


# Install the required package
# install.packages("fastDummies")



cleans<-cleans %>% mutate(goal_bin = ntile(goal, n=5),
                          goal_bin = as.factor(goal_bin))



###10. Binning Minage,Maxage of creators and projects
cleans<-cleans %>% mutate(minage_creator_bin = ntile(minage_creator, n=4),
                          minage_creator_bin = as.factor(minage_creator_bin))

cleans<-cleans %>% mutate(maxage_creator_bin = ntile(maxage_creator, n=4),
                          maxage_creator_bin = as.factor(maxage_creator_bin))

cleans<-cleans %>% mutate(minage_project_bin = ntile(minage_project, n=4),
                          minage_project_bin = as.factor(minage_project_bin))

cleans<-cleans %>% mutate(maxage_project_bin = ntile(maxage_project, n=4),
                          maxage_project_bin = as.factor(maxage_project_bin))
###11. Factor transformation
cleans <- cleans%>%
  mutate(
    location_type = as.factor(location_type),
    category_parent = as.factor(category_parent),
    color_foreground = as.factor(color_foreground),
    color_background = as.factor(color_background),
    accent_color = as.factor(accent_color),
    captions = as.factor(captions),
    contains_youtube = as.factor(contains_youtube)
  )

###12. Extracting  month year from launch date
cleans<-cleans%>%mutate(launch_month = format(launched_at, format="%m"),
                        created_month = format(created_at, format="%m"),
                        deadline_month = format(deadline, format="%m"),
                        launch_year = format(deadline, format="%Y"),
                        created_year = format(deadline, format="%Y"),
                        deadline_year = format(deadline, format="%Y"),
                        launch_month = as.factor(launch_month),
                        created_month = as.factor(created_month),
                        deadline_month = as.factor(deadline_month),
                        launch_year = as.factor(launch_year),
                        created_year = as.factor(created_year),
                        deadline_year = as.factor(deadline_year))

###13. Creating Top 5 states or not
##### Sort original dataframe by descending order of number of projects
cleans_sorted <- cleans %>%
  group_by(State) %>%
  mutate(count_state_wise = n()) %>%
  arrange(desc(count_state_wise))

##### Get names of creators of this dataframe
top_10_state_wise_filter<-unique(cleans_sorted$State)

##### Remove the initally created sorted dataframe
rm(cleans_sorted)

##### Filter just top 10 names and store them in a vector
top_10_state_wise_filter = c(head(top_10_state_wise_filter, n=5))

##### Mutate original data with inclusive exclusive of top 10 filter
cleans<-cleans%>%mutate(Top_5_State = ifelse(State%in%top_10_state_wise_filter,"YES","NO"),
                        Top_5_State = as.factor(Top_5_State))

##### Reward_Amount_processing

length_amounts<-sapply(strsplit(as.character(cleans$reward_amounts),","),FUN=function(x){length(x[x!="Null"])})
average_amount<-sapply(strsplit(as.character(cleans$reward_amounts),","),FUN=function(x){mean(as.numeric(x[x!="Null"]))})
min_amount<-sapply(strsplit(as.character(cleans$reward_amounts),","),FUN=function(x){min(as.numeric(x[x!="Null"]))})
max_amount<-sapply(strsplit(as.character(cleans$reward_amounts),","),FUN=function(x){max(as.numeric(x[x!="Null"]))})
median_amount<- sapply(strsplit(as.character(cleans$reward_amounts),","),FUN=function(x){median(as.numeric(x[x!="Null"]))})
cleans<-cleans%>%mutate(reward_amount_steps = length_amounts,
                        min_reward_amount = min_amount,
                        max_reward_amount = max_amount,
                        range_reward_amount = max_amount - min_amount,
                        average_reward_amount = average_amount)
cleans<-cleans %>%mutate(min_reward_amount = ifelse(is.na(min_reward_amount),mean(min_reward_amount,na.rm = TRUE),min_reward_amount),
                 max_reward_amount = ifelse(is.na(max_reward_amount),mean(max_reward_amount,na.rm = TRUE),max_reward_amount),
                 average_reward_amount = ifelse(is.na(average_reward_amount),mean(average_reward_amount,na.rm = TRUE),average_reward_amount),
                 range_reward_amount = ifelse(is.na(range_reward_amount),mean(range_reward_amount,na.rm = TRUE),range_reward_amount)
                                                    )

#### Tag Length Processing
length_tags<-sapply(strsplit(as.character(cleans$tag_names),"|"),FUN=function(x){length(x[x!="Null"])})
cleans<-cleans%>%mutate(length_tags = length_tags)
cleans<-cleans %>%mutate(length_tags = ifelse(is.na(length_tags),mean(length_tags,na.rm = TRUE),length_tags))

###Reward Description Paragraph


### Top Tags 

cleans<-cleans%>%mutate((separate(cleans,col = tag_names, 
          sep = "\\|",into = c('top_tag'),fill= 'right'))%>%
  group_by(top_tag)%>%
  mutate(count_top_tag = n())%>%
  ungroup()%>%
  mutate(istoptag = ifelse(count_top_tag>50,"YES","NO"),
         istoptag = ifelse(is.na(istoptag),"Missing",istoptag)
        ))

cleans<-cleans%>%mutate(count_top_tag = ifelse(is.na(count_top_tag),
                                          "Missing",count_top_tag),
                        top_tag = ifelse(is.na(top_tag),
                                               "Missing",top_tag),
                        
                          )
  
cleans<-cleans%>%mutate(top_tag = (ifelse(count_top_tag<100,"other",top_tag)))

cleans<-cleans%>%mutate(top_tag = as.factor(top_tag))

### Average Goal Per Day

cleans<-cleans%>%mutate(avg_goal_per_day = goal/as.numeric(funding_duration))

cleans_for_text_min<-cleans

view(head(cleans,n=10))
# ### 
# cleans<-cleans%>%mutate(reward_para = unlist(reward_descriptions))

#### Creating Dummy Variables

cleans<-dummy_cols(cleans,select_columns=c("goal_bin","maxage_creator_bin","minage_project_bin","category_parent","top_tag","istoptag"),remove_selected_columns = TRUE)

# names(cleans)[117] <- "category_parent_film_video"

cleans<-dummy_cols(cleans,select_columns=c("category_name","region","State","location_type","Top_5_State","deadline_year","launch_month", "created_month","deadline_month","launch_year","created_year",'isbwImg1',
'isTextPic',
'isLogoPic',
'isCalendarPic',
'isDiagramPic',
'isShapePic',
'contains_youtube',
'top_creator_quartile',
'top10_creators_by_num_projects',
'top10_creators_by_average_goal',
'category_in_top_10',
'fem_creators_greater_than_male_creators',
'fem_projects_greater_than_male_projects',
'afinn_positive_higher',
'Top_5_State'),remove_selected_columns = TRUE)



```


# Text Mining. 
**`This section primarily focuses on text mining project blurbs to obtain a vocabulary that can be used on the test dataset. Entirety of the training dataset blurbs are tokenized and a vocabulary is created. Below were the steps taken in creating a generalized vocabulary: 1. Stop words removed, punctuations removed, numbers removed, Each world appears atleast once in each category_parent, min count of word across the corpus  = 50.` **
## Text Mining Blurb of Each Project

```{r Text Mining Blurb of Each Project}

prep_fun = tolower

cleaning_tokenizer <- function(v) {
  v %>%
    removeNumbers %>% #remove all numbers
    removePunctuation %>% #remove all punctuation
    removeWords(stopwords(kind="en")) %>% #remove stopwords
    # stemDocument %>%
    word_tokenizer
}

tok_fun = cleaning_tokenizer

category_vec<-c('art',
'comics',
'crafts',
'dance',
'design',
'fashion',
'film & video',
'food',
'games',
'journalism',
'music',
'photography',
'publishing',
'technology',
'theater')


it_train = itoken(cleans_for_text_min$blurb,
                  preprocessor = prep_fun,
                  tokenizer = tok_fun,
                  ids = cleans_for_text_min$id,
                  progressbar = FALSE)

stop_words<-c('i', 'me', 'my', 'myself', 'we',
              'our', 'ours', 'ourselves', 'you', "you're",
              "you've", "you'll", "you'd", 'your', 'yours', 'yourself',
              'yourselves', 'he', 'him', 'his', 'himself', 'she', "she's",
              'her', 'hers', 'herself', 'it', "it's", 'its', 'itself',
              'they', 'them', 'their', 'theirs', 'themselves', 'what',
              'which', 'who', 'whom', 'this', 'that', "that'll", 'these',
              'those', 'am', 'is', 'are', 'was', 'were', 'be', 'been',
              'being', 'have', 'has', 'had', 'having', 'do', 'does', 'did', 'doing', 'a', 'an', 'the', 'and', 'but', 'if', 'or', 'because', 'as', 'until', 'while', 'of', 'at', 'by', 'for', 'with', 'about', 'against', 'between', 'into', 'through', 'during', 'before', 'after', 'above', 'below', 'to', 'from', 'up', 'down', 'in', 'out', 'on', 'off', 'over', 'under', 'again', 'further', 'then', 'once', 'here', 'there', 'when', 'where', 'why', 'how', 'all', 'any', 'both', 'each', 'few', 'more', 'most', 'other', 'some', 'such', 'no', 'nor', 'not', 'only', 'own', 'same', 'so', 'than', 'too', 'very', 's', 't', 'can', 'will', 'just', 'don', "don't", 'should', "should've", 'now', 'd', 'll', 'm', 'o', 're', 've', 'y', 'ain', 'aren', "aren't", 'couldn', "couldn't", 'didn', "didn't", 'doesn', "doesn't", 'hadn', "hadn't", 'hasn', "hasn't", 'haven', "haven't", 'isn', "isn't", 'ma', 'mightn', "mightn't", 'mustn', "mustn't", 'needn', "needn't", 'shan', "shan't", 'shouldn', "shouldn't", 'wasn', "wasn't", 'weren', "weren't", 'won', "won't", 'wouldn', "wouldn't")


vocab3 <- create_vocabulary(it_train, stopwords = stop_words, ngrams = c(1L,4L))
vocab3<-prune_vocabulary(vocab3,term_count_min = 50)

view(vocab3)

vocab_intersect<-vocab3

for (i in 1:length(category_vec)){
  category_n = category_vec[i]
  print(category_n)
  ##filter projects of that category
  cat_cleans<-cleans_for_text_min%>%filter(category_parent==category_n)
  cat_cleans_success<-cat_cleans%>%filter(success=="YES")
  # cat_cleans_success<-cat_cleans
  print(dim(cat_cleans_success))
  print(dim(vocab_intersect))
  prep_fun = tolower

  cleaning_tokenizer <- function(v) {
    v %>%
      removeNumbers %>% #remove all numbers
      removePunctuation %>% #remove all punctuation
      removeWords(stopwords(kind="en")) %>% #remove stopwords
      # stemDocument %>%
      word_tokenizer
  }

  tok_fun = cleaning_tokenizer


  ##Create vocabulary
  it_train = itoken(cat_cleans_success$blurb,
                    preprocessor = prep_fun,
                    tokenizer = tok_fun,
                    ids = cat_cleans_success$id,
                    progressbar = FALSE)

  stop_words<-c('i', 'me', 'my', 'myself', 'we',
                'our', 'ours', 'ourselves', 'you', "you're",
                "you've", "you'll", "you'd", 'your', 'yours', 'yourself',
                'yourselves', 'he', 'him', 'his', 'himself', 'she', "she's",
                'her', 'hers', 'herself', 'it', "it's", 'its', 'itself',
                'they', 'them', 'their', 'theirs', 'themselves', 'what',
                'which', 'who', 'whom', 'this', 'that', "that'll", 'these',
                'those', 'am', 'is', 'are', 'was', 'were', 'be', 'been',
                'being', 'have', 'has', 'had', 'having', 'do', 'does', 'did', 'doing', 'a', 'an', 'the', 'and', 'but',
                'if', 'or', 'because', 'as', 'until', 'while', 'of', 'at', 'by', 'for', 'with', 'about', 'against', 'between', 'into',
                'through', 'during', 'before', 'after', 'above', 'below', 'to', 'from', 'up', 'down', 'in', 'out', 'on', 'off', 'over',
                'under', 'again', 'further', 'then', 'once', 'here', 'there', 'when', 'where',
                'why', 'how', 'all', 'any', 'both', 'each', 'few', 'more', 'most', 'other', 'some', 'such', 'no', 'nor', 'not', 'only', 'own',
                'same', 'so', 'than', 'too', 'very', 's', 't', 'can', 'will', 'just', 'don', "don't", 'should', "should've", 'now', 'd', 'll',
                'm', 'o', 're', 've', 'y', 'ain', 'aren', "aren't", 'couldn', "couldn't",
                'didn', "didn't", 'doesn', "doesn't", 'hadn', "hadn't", 'hasn', "hasn't", 'haven', "haven't", 'isn', "isn't", 'ma', 'mightn', "mightn't",
                'mustn', "mustn't", 'needn', "needn't", 'shan', "shan't", 'shouldn', "shouldn't", 'wasn',
                "wasn't", 'weren', "weren't", 'won', "won't", 'wouldn', "wouldn't")


  vocab_filtered <- create_vocabulary(it_train, stopwords = stop_words, ngrams = c(1L,4L))

  ## Check Intersection and Store it Back in a single Vocabulary
  vocab_intersect<-vocab_intersect%>%filter(term %in% vocab_filtered$term)

}

final_vocab= vocab3%>%filter(term %in% vocab_intersect$term)
final_vectorizer = vocab_vectorizer(final_vocab)

### Tokenizing and creating DTM for entire training set.
it_train = itoken(cleans$blurb,
                  preprocessor = prep_fun,
                  tokenizer = tok_fun,
                  ids = cleans$id,
                  progressbar = FALSE)

dtm_cleans = create_dtm(it_train, final_vectorizer)
dim(dtm_cleans)

tfidf = TfIdf$new()
dtm_cleans_tfidf = fit_transform(dtm_cleans, tfidf)
dim(dtm_cleans_tfidf)

```


```{r Predict using Text Features on Entire Training Data}

## Running a regularized logistic regression to get predictions.
tr_x<-dtm_cleans_tfidf
tr_y<-ifelse(cleans$success=="YES",1,0)


grid <- 10^seq(7,-7,length=100)
k<-5
cv.out.ridge <- cv.glmnet(tr_x, tr_y, family="binomial", alpha=0, lambda=grid, nfolds=k)

plot(cv.out.ridge)
bestlam_ridge <- cv.out.ridge$lambda.min
pred_ridge <- predict(cv.out.ridge, s=bestlam_ridge, newx = tr_x,type="response")

## Binding to original dataset as an added feature
cleans<-cbind(cleans,pred_ridge)
cleans<-rename(cleans, "numerical_pred_ridge_blurb" = "s1")

```


```{r Train Test Split for Model Creation, Evaluation and Selection}
cleans<-rename(cleans, "category_parent_film_video"="category_name_Film  Video" )

base_data1 <- cleans%>%
  select(goal,average_goal_by_cat_parent,
numfaces_project,
numfaces_creator,
male_project,
male_creator,
female_project,
female_creator,
smiling_project,
smiling_creator,
minage_project,
minage_creator,
maxage_project,
maxage_creator,
num_words,
avg_wordlengths,
sentence_counter,
avgsentencelength,
avgsyls,
grade_level,
afinn_pos,
afinn_neg,
ADV,
NOUN,
ADP,
PRT,
DET,
PRON,
VERB,
NUM,
CONJ,
ADJ,
count,
quantile_rank,
target_duration,
funding_duration,
count_location_type,
afinn_diff,
reward_amount_steps,
min_reward_amount,
max_reward_amount,
range_reward_amount,
average_reward_amount,
length_tags,
count_top_tag,
avg_goal_per_day,
goal_bin_1,
goal_bin_2,
goal_bin_3,
goal_bin_4,
goal_bin_5,
maxage_creator_bin_1,
maxage_creator_bin_2,
maxage_creator_bin_3,
maxage_creator_bin_4,
minage_project_bin_1,
minage_project_bin_2,
minage_project_bin_3,
minage_project_bin_4,
category_parent_art,
category_parent_comics,
category_parent_crafts,
category_parent_dance,
category_parent_design,
category_parent_fashion,
category_parent_film_video,
category_parent_food,
category_parent_games,
category_parent_journalism,
category_parent_music,
category_parent_photography,
category_parent_publishing,
category_parent_technology,
category_parent_theater,
top_tag_cartoon,
top_tag_design,
top_tag_drawing,
top_tag_food,
top_tag_grass,
top_tag_indoor,
top_tag_Missing,
top_tag_other,
top_tag_outdoor,
top_tag_person,
top_tag_screenshot,
top_tag_sketch,
top_tag_sky,
top_tag_text,
top_tag_tree,
istoptag_NO,
istoptag_YES,
region_ENCentral,
region_ESCentral,
region_MidAtl,
region_Mountain,
region_NewEng,
region_Pacific,
region_SouthAtl,
region_WNCentral,
region_WSCentral,
State_ak,
State_al,
State_ar,
State_az,
State_ca,
State_co,
State_ct,
State_dc,
State_de,
State_fl,
State_ga,
State_hi,
State_ia,
State_id,
State_il,
State_in,
State_ks,
State_ky,
State_la,
State_ma,
State_md,
State_me,
State_mi,
State_mn,
State_mo,
State_ms,
State_mt,
State_nc,
State_nd,
State_ne,
State_nh,
State_nj,
State_nm,
State_nv,
State_ny,
State_oh,
State_ok,
State_one,
State_or,
State_pa,
State_ri,
State_sc,
State_sd,
State_tn,
State_tx,
State_us,
State_ut,
State_va,
State_vt,
State_wa,
State_wi,
State_wv,
State_wy,
location_type_Other,
location_type_Town,
Top_5_State_NO,
Top_5_State_YES,
deadline_year_2014,
launch_month_07,
launch_month_08,
launch_month_09,
launch_month_10,
launch_month_11,
created_month_01,
created_month_02,
created_month_03,
created_month_04,
created_month_05,
created_month_06,
created_month_07,
created_month_08,
created_month_09,
created_month_10,
created_month_11,
created_month_12,
deadline_month_09,
deadline_month_10,
deadline_month_11,
deadline_month_12,
launch_year_2014,
created_year_2014,
isbwImg1_FALSE,
isbwImg1_Missing,
isbwImg1_TRUE,
isTextPic_0,
isTextPic_1,
isTextPic_Missing,
isLogoPic_0,
isLogoPic_1,
isLogoPic_Missing,
isCalendarPic_0,
isCalendarPic_1,
isCalendarPic_Missing,
isDiagramPic_0,
isDiagramPic_1,
isDiagramPic_Missing,
isShapePic_0,
isShapePic_1,
isShapePic_Missing,
contains_youtube_0,
contains_youtube_1,
top_creator_quartile_NO,
top_creator_quartile_YES,
top10_creators_by_num_projects_NO,
top10_creators_by_num_projects_YES,
top10_creators_by_average_goal_NO,
top10_creators_by_average_goal_YES,
category_in_top_10_NO,
category_in_top_10_YES,
fem_creators_greater_than_male_creators_NO,
fem_creators_greater_than_male_creators_YES,
fem_projects_greater_than_male_projects_NO,
fem_projects_greater_than_male_projects_YES,
afinn_positive_higher_NO,
afinn_positive_higher_YES,
numerical_pred_ridge_blurb,
success
  )

train_withterms <- base_data1

set.seed(1)

tr_inds <- sample(nrow(train_withterms), 0.7*nrow(train_withterms))
train_withterms<-rename(train_withterms, funding_goal = goal)

train_withterms<- train_withterms%>%mutate(funding_duration = as.numeric(funding_duration),
target_duration = as.numeric(target_duration))

train_withterms$success <- ifelse(train_withterms$success=="YES",1,0)

tr <- train_withterms[tr_inds,]
va <- train_withterms[-tr_inds,]
```


```{r Create Models: Model 1 Regularized Logistic Regression}

##2. Regularized Logistic Regression
# 
# log1 <- glm(success~., data = tr, family = "binomial")
# probs_success <- predict(log1, newdata = va, type = "response")
# 
# classifications <- ifelse(probs_success > .5, "YES", "NO")
# correct <- ifelse(classifications == va$success, 1, 0)
# acc <- sum(correct)/length(correct)
# 
# #### Regularized Logistic Regression
base_data1_x <- model.matrix(success~.,base_data1)
base_data1_y <- base_data1$success

##### Train Test Split
train <- sample(nrow(base_data1),.7*nrow(base_data1))
x_train <- base_data1_x[train,]
x_valid <- base_data1_x[-train,]

y_train <- base_data1_y[train]
y_valid <- base_data1_y[-train]
# 
# #family="binomial" yields logistic regression; family="gaussian" yields linear regression
# #alpha = 1 yields the lasso penalty, and alpha = 0 the ridge penalty
# #basic, default
# glm.out.ridge <- glmnet(x_train, y_train, alpha = 0, family="binomial")
# # glm.out.lasso <- glmnet(x_train, y_train, alpha = 1, family="binomial")
# # 
# # #shows coefficient values vs. lambda
# plot(glm.out.ridge, xvar = "lambda")
# # plot(glm.out.lasso, xvar = "lambda")

#Hyperparameter Tuning using Grid Search and Cross Validation for Logistic Regression
grid <- 10^seq(10,-10,length=100)
grid

#glmnet automatically does cross-validation for you, you just need to specify k. Let's try k=5.
k<-5

#family="binomial" yields logistic regression; family="gaussian" yields linear regression
#alpha = 1 yields the lasso penalty, and alpha= 0 the ridge penalty
cv.out <- cv.glmnet(x_train, y_train, family="binomial", alpha=0, lambda=grid, nfolds=k)
# plot(cv.out)


#get the lambda that gave the lowest cross-validated error
bestlam <- cv.out$lambda.min
coeffs <- coef(cv.out, s = "lambda.min")
# coeffs

#you have to add type="response" to get probabilities for logistic regression
pred <- predict(cv.out, s=bestlam, newx = x_valid,type="response")

#you can also plot a fitting curve
lambdas <- cv.out$lambda
errors <- cv.out$cvm

# plot(lambdas, errors)
pred_class <- ifelse(pred>.5,1,0)
pred_acc <- mean(ifelse(pred_class==ifelse(va$success=="YES",1,0),1,0))
pred_acc
#with this particular set of lambdas, you can see the curve easier if you plot them on a log-log scale
plot(log(lambdas), errors)



```


```{r Create Models: Model 2 GBM}
##1. GBM

boost.mod <- gbm(success~.,data=tr,
                 distribution="bernoulli",
                 n.trees=750,
                interaction.depth = 4,
                shrinkage = 0.1,
                )

boost_preds <- predict(boost.mod,newdata=va,type='response',n.trees=750)

#classify with a cutoff and compute accuracy
boost_class <- ifelse(boost_preds>.5,1,0)
boost_acc <- mean(ifelse(boost_class==va$success,1,0))
boost_acc
summary.gbm(boost.mod)

### Hyperparameter Tuning


# # Cross Validation and Hyperparameter Tuning
# grid_search <- function(){
# 
#  
#   # depth_choose <- c(2, 5, 10, 20, 50, 100,250,500,1000)
#   depth_choose <- c(2,3,4)
#   ntrees_choose <- c(500,750,1000,1250,1500)
#   eta_choose <- c(0.01,0.02,0.03,0.04,0.05,0.06,0.07,0.08,0.09,0.1)
# 
#   #nested loops to tune these three parameters
#   print('depth, ntrees, eta, accuracy')
#   for(i in c(1:length(depth_choose))){
#     for(j in c(1:length(ntrees_choose))){
#       for(k in c(1:length(eta_choose))){
#         thisdepth <- depth_choose[i]
#         thisntrees <- ntrees_choose[j]
#         thiseta <- eta_choose[k]
# 
#         boost.mod <- gbm(success~.,data=tr,
#                          distribution="bernoulli",
#                          n.trees=thisntrees,
#                          interaction.depth = thisdepth,
#                          shrinkage = thiseta,
#                          cv.folds = 3,
#                          verbose = TRUE,
#                          class.stratify.cv = TRUE,
#                          n.cores = NULL)
# 
#         boost_preds <- predict(boost.mod,newdata=va,type='response',n.trees=1000)
# 
#         #classify with a cutoff and compute accuracy
#         boost_class <- ifelse(boost_preds>.5,1,0)
#         boost_acc <- mean(ifelse(boost_class==va$success,1,0))
# 
# 
#         #print the performance for every combination
#         print(paste(thisdepth, thisnrounds, thiseta, boost_acc, sep = ", "))
# 
#       }
#     }
#   }
# }
# grid_search()



```


```{r Create Models: Model 3 RF}
# rf.mod <- randomForest(success~.,
#                        data=base_data1,
#                        subset=tr_inds,
#                        mtry=15, ntree=850,
#                        importance=TRUE)


# 
# 
# 
# importance_vars<-importance(rf.mod)
# view(importance_vars)
# rf_preds <- predict(rf.mod, newdata=va)
# 
# rf_acc <- mean(ifelse(rf_preds==va$success,1,0))
# rf_acc


```
# ###Iteration Log for RF

# ####1. 25 minutes to train 70% of big dataset mtry = 4, ntree = 1000
# ####2. 25 minutes to train 70% of big dataset mtry = 4, ntree = 700


```{r Create Models: Model 4 XGBoost}
tr_x<-tr[,-217]
va_x<-va[,-217]

tr_y<-tr$success
va_y<-va$success

boost_train_matrix <- data.matrix(sapply(tr_x, as.numeric))
boost_valid_matrix <- data.matrix(sapply(va_x, as.numeric))

# bst <- xgboost(data = boost_train_matrix, label = tr_y, max.depth = 4, eta = 0.1, nrounds = 700,  objective = "binary:logistic")
# 
# 
# bst_pred <- predict(bst, boost_valid_matrix)
# bst_classifications <- ifelse(bst_pred > 0.5, 1, 0)
# bst_acc <- mean(ifelse(bst_classifications == va_y, 1, 0))
# bst_acc
# 
# vip(bst,num_features = 40)

#Hyper Parameter Tuning

grid_search <- function(){

  #three hyperparameters can possibly really change predictive performance of xgboost (although maybe not)
  # depth_choose <- c(2, 5, 10, 20, 50, 100,250,500,1000)
  depth_choose <- c(3,4,5,7)
  nrounds_choose <- c( 200,250,400,500,700,750,900,1000,1500)
  eta_choose <- c(0.05,0.15,0.25,0.35,0.5,0.65,0.8,0.85,0.9,0.95)
  accuracy<-vector(10)

  #nested loops to tune these three parameters
  print('depth, nrounds, eta, accuracy')

      for(k in c(1:length(eta_choose))){
        thisdepth <- 6
        thisnrounds <- 700
        thiseta <- eta_choose[k]

        inner_bst <- xgboost(data = boost_train_matrix, label = tr_y, max.depth = thisdepth, eta = thiseta, nrounds = thisnrounds,  objective = "binary:logistic", verbosity = 0, verbose = 0)

        inner_bst_pred <- predict(inner_bst, boost_valid_matrix)
        inner_bst_classifications <- ifelse(inner_bst_pred > 0.5, 1, 0)
        inner_bst_acc <- mean(ifelse(inner_bst_classifications == va_y, 1, 0))

        #print the performance for every combination
        print(paste(thisdepth, thisnrounds, thiseta, inner_bst_acc, sep = ", "))

      }
  
}
    
grid_search()
ggsave("plot_xg_boost.jpg",plot(eta_choose,inner_bst_acc))

```


```{r Create Models: Model 5 Catboost}
#### Catboost
library(catboost)

## X Values

# tr$top_tag = as.factor(tr$top_tag)
# va$top_tag = as.factor(va$top_tag)

X_train<-tr[,-217]
X_valid<-va[,-217]

X_train <- as.matrix(sapply(X_train, as.numeric))
X_valid <- as.matrix(sapply(X_valid, as.numeric))

##Y Values
# y_train<-ifelse(tr[,38]=="YES",1,0)
y_train<-tr[,217]
# y_valid<-ifelse(va[,38]=="YES",1,0)
y_valid<-va[,217]

train_pool <- catboost.load_pool(data = X_train, label = y_train)
test_pool <- catboost.load_pool(data = X_valid, label = y_valid)
#  
# 
# learning_rates<-c(0.06,0.07,0.08,0.09,0.1,0.11,0.12)
# iterations<-c(1250)
# depth<-c(4,5,6,7)
# 
# for(i in (1:length(iterations)))
#   {
#     for (j in (1:length(learning_rates)))
#       {
#         for (k in (1:length(depth)))
#         {
#                   lr<-learning_rates[j]
#                   it<-iterations[i]
#                   dp<-depth[k]
#                    print(it)
#                   print(lr)
#                   print(dp)
#                   params <- list(iterations=it,
#                                 learning_rate=lr,
#                                 depth=dp,
#                                 loss_function='Logloss',
#                                 eval_metric='Accuracy',
#                                 random_seed = 55,
#                                 od_type='Iter',
#                                 metric_period = 50,
#                                 od_wait=20,
#                                 use_best_model=TRUE,
#                                 boosting_type = "Ordered")
#                 model <- catboost.train(train_pool, test_pool, params)
# 
#                 
#         }
#       }
#     }


# ## Single Model for Feature Importances

params <- list(iterations=2200,
               learning_rate=0.03,
               depth=6,
               loss_function='Logloss',
               eval_metric='Accuracy',
               random_seed = 42,
               metric_period = 50,
               od_type = "Iter",
               use_best_model=TRUE,
               boosting_type = "Ordered"
               )

model <- catboost.train(train_pool, test_pool, params)
catboost.get_feature_importance(model,
                                pool = NULL,
                                type = 'FeatureImportance',
                                thread_count = -1)


```


```{r Create Models: Model 6 Light GBM}
tr_x<-tr[,-217]
va_x<-va[,-217]

tr_y<-tr$success
va_y<-va$success

boost_train_matrix <- data.matrix(sapply(tr_x, as.numeric))
boost_valid_matrix <- data.matrix(sapply(va_x, as.numeric))

lgb.grid = list(objective = "binary",
                metric = "auc",
                min_sum_hessian_in_leaf = 1,
                feature_fraction = 0.7,
                bagging_fraction = 0.7,
                bagging_freq = 5,
                min_data = 100,
                max_bin = 50,
                lambda_l1 = 8,
                lambda_l2 = 1.3,
                min_data_in_bin=100,
                min_gain_to_split = 10,
                min_data_in_leaf = 30,
                is_unbalance = TRUE)

#Fitting the model
lgb.model = lgb.train(params = lgb.grid, data = boost_train_matrix, learning_rate = 0.02,
                      num_leaves = 25, num_threads = 2 , nrounds = best.iter,
                      eval_freq = 20,
                      categorical_feature = categoricals.vec)

lgb_preds <- predict(lgb.model,boost_valid_matrix)
lgb_classifications <- ifelse(lgb_pred > 0.5, 1, 0)
lgb_acc <- mean(ifelse(lgb_classifications == va_y, 1, 0))
lgb_acc
```


## Deployment on Test Set

```{r Feature Engineering of Test Data, echo = FALSE}
trains<-testxs

cleans <- trains%>%
  mutate(
    # location_type = as.factor(location_type),
    region = as.factor(region),
    # category_parent = as.factor(category_parent),
    # color_foreground = as.factor(color_foreground),
    # color_background = as.factor(color_background),
    # accent_color = as.factor(accent_color),
    # captions = as.factor(captions),
    deadline = as.Date(deadline)
  )

### Category wise Average Goal
cleans<-cleans%>%
  group_by(category_parent) %>% mutate(average_goal_by_cat_parent = mean(goal)) %>%ungroup()

cleans <- cleans %>%
  group_by(creator_name) %>%
  mutate(count = n()) %>%
  ungroup() %>%
  mutate(quantile_rank = ntile(count, 4),
         top_creator_quartile = as.factor(ifelse(quantile_rank == 1, "YES", "NO")))


#### Top 10 Creator Names by number of projects
##### Sort original dataframe by descending order of number of projects
cleans_sorted <- cleans %>%
  group_by(creator_name) %>%
  mutate(count_creator_name = n()) %>%
  arrange(desc(count_creator_name))

##### Get names of creators of this dataframe
top_10_creator_name_filter<-unique(cleans_sorted$creator_name)

##### Remove the initally created sorted dataframe
rm(cleans_sorted)

##### Filter just top 10 names and store them in a vector
top_10_creator_name_filter = c(head(top_10_creator_name_filter, n=10))

##### Mutate original data with inclusive exclusive of top 10 filter
cleans<-cleans%>%mutate(top10_creators_by_num_projects = ifelse(creator_name%in%top_10_creator_name_filter,"YES","NO"),
                        top10_creators_by_num_projects = as.factor(top10_creators_by_num_projects))


#### Top 10 Creator Names by average goal

average_goal_by_creator <- cleans %>%group_by(creator_name)%>%
  mutate (average_goal = mean(goal))%>%arrange(desc(average_goal))

##### Get names of creators of this dataframe
top_10_creator_name_filter<-unique(average_goal_by_creator$creator_name)

##### Remove the initally created sorted dataframe
rm(average_goal_by_creator)

##### Filter just top 10 names and store them in a vector
top_10_creator_name_filter = c(head(top_10_creator_name_filter, n=10))

##### Mutate original data with inclusive exclusive of top 10 filter
cleans<-cleans%>%mutate(top10_creators_by_average_goal = ifelse(creator_name%in%top_10_creator_name_filter,"YES","NO"),
                        top10_creators_by_average_goal=as.factor(top10_creators_by_average_goal))



### 2. Duration between created and launched at and Duration between launched at and deadline 
cleans <- cleans %>%
  mutate(created_at = as.Date(created_at),
         launched_at = as.Date(launched_at),
         target_duration = launched_at - created_at,
         funding_duration = deadline - launched_at)

###3. Location Slug:- Separate Name and City
cleans <- cleans %>%
  separate(location_slug, c("City", "State"), sep = -3) %>%
  mutate( City = as.character(gsub("-"," ", City)),
    State = as.character(gsub("-","",State)),
    State = as.factor(State),
    City = as.factor(City))
    # State = as.factor(State))

cleans <- cleans %>%
  left_join(income_per_capita, by = "State")

###4. Location Type:- Group less frequently occuring location types

cleans<-cleans%>%group_by(location_type)%>%mutate(count_location_type = n())%>%ungroup()%>% mutate(location_type = ifelse(count_location_type<500,"Other",location_type),
                                                                                                   location_type = as.factor(location_type),
                                                                                                   region = as.factor(region),
                                                                                                   category_name = as.factor(category_name))

###5. Category within Category Parent - Find if category is top in the parent or not
category_name_sorted<-cleans%>%group_by(category_parent,category_name)%>%mutate(count_category_name = n())%>%arrange(desc(count_category_name))


##### Get names of category of this dataframe
top_10_category_name_filter<-unique(category_name_sorted$category_name)


##### Remove the initally created sorted dataframe
rm(category_name_sorted)

##### Filter just top 10 names and store them in a vector
top_10_category_name_filter = c(head(top_10_category_name_filter, n=10))

##### Mutate original data with inclusive exclusive of top 10 filter
cleans<-cleans%>%mutate(category_in_top_10 = ifelse(category_name%in%top_10_category_name_filter,"YES","NO"),
                        category_in_top_10 = as.factor(category_in_top_10))

###5. Female Creator> Male Creator? and Female Project>Male Project?
cleans<-cleans%>%mutate(fem_creators_greater_than_male_creators = ifelse(female_creator>male_creator,"YES","NO"),
                        fem_creators_greater_than_male_creators = as.factor(fem_creators_greater_than_male_creators))

cleans<-cleans%>%mutate(fem_projects_greater_than_male_projects = ifelse(female_project>male_project,"YES","NO"),
                        fem_projects_greater_than_male_projects=as.factor(fem_projects_greater_than_male_projects))


###6. Replace all NAs in (isTextPic,...) with "Missing"
# vectoreplace<-c("isbwImg1","isShapePic","isDiagramPic","isCalendarPic","isLogoPic","isTextPic","captions","color_foreground","color_background","accent_color")

cleans$isbwImg1[is.na(cleans$isbwImg1)]<-"Missing"
cleans$isShapePic[is.na(cleans$isShapePic)]<-"Missing"
cleans$isDiagramPic[is.na(cleans$isDiagramPic)]<-"Missing"
cleans$isCalendarPic[is.na(cleans$isCalendarPic)]<-"Missing"
cleans$isTextPic[is.na(cleans$isTextPic)]<-"Missing"
cleans$isLogoPic[is.na(cleans$isLogoPic)]<-"Missing"
cleans$captions[is.na(cleans$captions)]<-"Missing"
cleans$color_foreground[is.na(cleans$color_foreground)]<-"Missing"
cleans$color_background[is.na(cleans$color_background)]<-"Missing"
cleans$accent_color[is.na(cleans$accent_color)]<-"Missing"

###7. Create Dummy Variables for Tag Names

# cleans<-cSplit_e(cleans, "tag_names", "|", type = "character", fill = 0, drop = T)

# Problem Encountered: Too Many Tags leading to too many columns - Cannot allocate it in a dataframe

###8. affin_positive and affin_negative

cleans<-cleans%>%mutate(afinn_diff = afinn_pos - afinn_neg)

cleans<-cleans%>%mutate(afinn_positive_higher = ifelse(afinn_pos>afinn_neg,"YES","NO"),
                        afinn_positive_higher = as.factor(afinn_positive_higher))


###9. Binning Goal Variable


# Install the required package
# install.packages("fastDummies")



cleans<-cleans %>% mutate(goal_bin = ntile(goal, n=5),
                          goal_bin = as.factor(goal_bin))



###10. Binning Minage,Maxage of creators and projects
cleans<-cleans %>% mutate(minage_creator_bin = ntile(minage_creator, n=4),
                          minage_creator_bin = as.factor(minage_creator_bin))

cleans<-cleans %>% mutate(maxage_creator_bin = ntile(maxage_creator, n=4),
                          maxage_creator_bin = as.factor(maxage_creator_bin))

cleans<-cleans %>% mutate(minage_project_bin = ntile(minage_project, n=4),
                          minage_project_bin = as.factor(minage_project_bin))

cleans<-cleans %>% mutate(maxage_project_bin = ntile(maxage_project, n=4),
                          maxage_project_bin = as.factor(maxage_project_bin))
###11. Factor transformation
cleans <- cleans%>%
  mutate(
    location_type = as.factor(location_type),
    category_parent = as.factor(category_parent),
    color_foreground = as.factor(color_foreground),
    color_background = as.factor(color_background),
    accent_color = as.factor(accent_color),
    captions = as.factor(captions),
    contains_youtube = as.factor(contains_youtube)
  )

###12. Extracting  month year from launch date
cleans<-cleans%>%mutate(launch_month = format(launched_at, format="%m"),
                        created_month = format(created_at, format="%m"),
                        deadline_month = format(deadline, format="%m"),
                        launch_year = format(deadline, format="%Y"),
                        created_year = format(deadline, format="%Y"),
                        deadline_year = format(deadline, format="%Y"),
                        launch_month = as.factor(launch_month),
                        created_month = as.factor(created_month),
                        deadline_month = as.factor(deadline_month),
                        launch_year = as.factor(launch_year),
                        created_year = as.factor(created_year),
                        deadline_year = as.factor(deadline_year))

###13. Creating Top 5 states or not
##### Sort original dataframe by descending order of number of projects
cleans_sorted <- cleans %>%
  group_by(State) %>%
  mutate(count_state_wise = n()) %>%
  arrange(desc(count_state_wise))

##### Get names of creators of this dataframe
top_10_state_wise_filter<-unique(cleans_sorted$State)

##### Remove the initally created sorted dataframe
rm(cleans_sorted)

##### Filter just top 10 names and store them in a vector
top_10_state_wise_filter = c(head(top_10_state_wise_filter, n=5))

##### Mutate original data with inclusive exclusive of top 10 filter
cleans<-cleans%>%mutate(Top_5_State = ifelse(State%in%top_10_state_wise_filter,"YES","NO"),
                        Top_5_State = as.factor(Top_5_State))

##### Reward_Amount_processing

length_amounts<-sapply(strsplit(as.character(cleans$reward_amounts),","),FUN=function(x){length(x[x!="Null"])})
average_amount<-sapply(strsplit(as.character(cleans$reward_amounts),","),FUN=function(x){mean(as.numeric(x[x!="Null"]))})
min_amount<-sapply(strsplit(as.character(cleans$reward_amounts),","),FUN=function(x){min(as.numeric(x[x!="Null"]))})
max_amount<-sapply(strsplit(as.character(cleans$reward_amounts),","),FUN=function(x){max(as.numeric(x[x!="Null"]))})
median_amount<- sapply(strsplit(as.character(cleans$reward_amounts),","),FUN=function(x){median(as.numeric(x[x!="Null"]))})
cleans<-cleans%>%mutate(reward_amount_steps = length_amounts,
                        min_reward_amount = min_amount,
                        max_reward_amount = max_amount,
                        range_reward_amount = max_amount - min_amount,
                        average_reward_amount = average_amount)
cleans<-cleans %>%mutate(min_reward_amount = ifelse(is.na(min_reward_amount),mean(min_reward_amount,na.rm = TRUE),min_reward_amount),
                 max_reward_amount = ifelse(is.na(max_reward_amount),mean(max_reward_amount,na.rm = TRUE),max_reward_amount),
                 average_reward_amount = ifelse(is.na(average_reward_amount),mean(average_reward_amount,na.rm = TRUE),average_reward_amount),
                 range_reward_amount = ifelse(is.na(range_reward_amount),mean(range_reward_amount,na.rm = TRUE),range_reward_amount)
                                                    )

#### Tag Length Processing
length_tags<-sapply(strsplit(as.character(cleans$tag_names),"|"),FUN=function(x){length(x[x!="Null"])})
cleans<-cleans%>%mutate(length_tags = length_tags)
cleans<-cleans %>%mutate(length_tags = ifelse(is.na(length_tags),mean(length_tags,na.rm = TRUE),length_tags))

### Top Tags 

cleans<-cleans%>%mutate((separate(cleans,col = tag_names, 
          sep = "\\|",into = c('top_tag'),fill= 'right'))%>%
  group_by(top_tag)%>%
  mutate(count_top_tag = n())%>%
  ungroup()%>%
  mutate(istoptag = ifelse(count_top_tag>50,"YES","NO"),
         istoptag = ifelse(is.na(istoptag),"Missing",istoptag)
        ))

cleans<-cleans%>%mutate(count_top_tag = ifelse(is.na(count_top_tag),
                                          "Missing",count_top_tag),
                        top_tag = ifelse(is.na(top_tag),
                                               "Missing",top_tag),
                        
                          )
  
cleans<-cleans%>%mutate(top_tag = (ifelse(count_top_tag<100,"other",top_tag)))

cleans<-cleans%>%mutate(top_tag = as.factor(top_tag))

### Average Goal Per Day

cleans<-cleans%>%mutate(avg_goal_per_day = goal/as.numeric(funding_duration))
#### Creating Dummy Variables

cleans<-dummy_cols(cleans,select_columns=c("goal_bin","maxage_creator_bin","minage_project_bin","category_parent","top_tag","istoptag"),remove_selected_columns = TRUE)

# names(cleans)[117] <- "category_parent_film_video"

cleans<-dummy_cols(cleans,select_columns=c("category_name","region","State","location_type","Top_5_State","deadline_year","launch_month", "created_month","deadline_month","launch_year","created_year",'isbwImg1',
'isTextPic',
'isLogoPic',
'isCalendarPic',
'isDiagramPic',
'isShapePic',
'contains_youtube',
'top_creator_quartile',
'top10_creators_by_num_projects',
'top10_creators_by_average_goal',
'category_in_top_10',
'fem_creators_greater_than_male_creators',
'fem_projects_greater_than_male_projects',
'afinn_positive_higher',
'Top_5_State'),remove_selected_columns = TRUE)

##Tokenizing test and creating dtm
it_train = itoken(cleans$blurb,
                  preprocessor = prep_fun,
                  tokenizer = tok_fun,
                  ids = cleans$id,
                  progressbar = FALSE)


dtm_cleans = create_dtm(it_train, final_vectorizer)
dim(dtm_cleans)

tfidf = TfIdf$new()
dtm_cleans_tfidf = fit_transform(dtm_cleans, tfidf)

###Predicting blurb ridge predictions

pred_ridge <- predict(cv.out.ridge, s=bestlam_ridge, newx = dtm_cleans_tfidf,type="response")
class_ridge<-ifelse(pred_ridge>0.5,1,0)

cleans<-cbind(cleans,pred_ridge)
cleans<-rename(cleans, "numerical_pred_ridge_blurb" = "s1")
cleans<-cbind(cleans,class_ridge)

cleans<-subset(cleans,select = -c(s1))

cleans<-rename(cleans, "category_parent_film_video"="category_name_Film  Video")

base_data2 <- cleans%>%
  select(goal,average_goal_by_cat_parent,
numfaces_project,
numfaces_creator,
male_project,
male_creator,
female_project,
female_creator,
smiling_project,
smiling_creator,
minage_project,
minage_creator,
maxage_project,
maxage_creator,
num_words,
avg_wordlengths,
sentence_counter,
avgsentencelength,
avgsyls,
grade_level,
afinn_pos,
afinn_neg,
ADV,
NOUN,
ADP,
PRT,
DET,
PRON,
VERB,
NUM,
CONJ,
ADJ,
count,
quantile_rank,
target_duration,
funding_duration,
count_location_type,
afinn_diff,
reward_amount_steps,
min_reward_amount,
max_reward_amount,
range_reward_amount,
average_reward_amount,
length_tags,
count_top_tag,
avg_goal_per_day,
goal_bin_1,
goal_bin_2,
goal_bin_3,
goal_bin_4,
goal_bin_5,
maxage_creator_bin_1,
maxage_creator_bin_2,
maxage_creator_bin_3,
maxage_creator_bin_4,
minage_project_bin_1,
minage_project_bin_2,
minage_project_bin_3,
minage_project_bin_4,
category_parent_art,
category_parent_comics,
category_parent_crafts,
category_parent_dance,
category_parent_design,
category_parent_fashion,
category_parent_film_video,
category_parent_food,
category_parent_games,
category_parent_journalism,
category_parent_music,
category_parent_photography,
category_parent_publishing,
category_parent_technology,
category_parent_theater,
top_tag_cartoon,
top_tag_design,
top_tag_drawing,
top_tag_food,
top_tag_grass,
top_tag_indoor,
top_tag_Missing,
top_tag_other,
top_tag_outdoor,
top_tag_person,
top_tag_screenshot,
top_tag_sketch,
top_tag_sky,
top_tag_text,
top_tag_tree,
istoptag_NO,
istoptag_YES,
region_ENCentral,
region_ESCentral,
region_MidAtl,
region_Mountain,
region_NewEng,
region_Pacific,
region_SouthAtl,
region_WNCentral,
region_WSCentral,
State_ak,
State_al,
State_ar,
State_az,
State_ca,
State_co,
State_ct,
State_dc,
State_de,
State_fl,
State_ga,
State_hi,
State_ia,
State_id,
State_il,
State_in,
State_ks,
State_ky,
State_la,
State_ma,
State_md,
State_me,
State_mi,
State_mn,
State_mo,
State_ms,
State_mt,
State_nc,
State_nd,
State_ne,
State_nh,
State_nj,
State_nm,
State_nv,
State_ny,
State_oh,
State_ok,
State_one,
State_or,
State_pa,
State_ri,
State_sc,
State_sd,
State_tn,
State_tx,
State_us,
State_ut,
State_va,
State_vt,
State_wa,
State_wi,
State_wv,
State_wy,
location_type_Other,
location_type_Town,
Top_5_State_NO,
Top_5_State_YES,
deadline_year_2014,
launch_month_07,
launch_month_08,
launch_month_09,
launch_month_10,
launch_month_11,
created_month_01,
created_month_02,
created_month_03,
created_month_04,
created_month_05,
created_month_06,
created_month_07,
created_month_08,
created_month_09,
created_month_10,
created_month_11,
created_month_12,
deadline_month_09,
deadline_month_10,
deadline_month_11,
deadline_month_12,
launch_year_2014,
created_year_2014,
isbwImg1_FALSE,
isbwImg1_Missing,
isbwImg1_TRUE,
isTextPic_0,
isTextPic_1,
isTextPic_Missing,
isLogoPic_0,
isLogoPic_1,
isLogoPic_Missing,
isCalendarPic_0,
isCalendarPic_1,
isCalendarPic_Missing,
isDiagramPic_0,
isDiagramPic_1,
isDiagramPic_Missing,
isShapePic_0,
isShapePic_1,
isShapePic_Missing,
contains_youtube_0,
contains_youtube_1,
top_creator_quartile_NO,
top_creator_quartile_YES,
top10_creators_by_num_projects_NO,
top10_creators_by_num_projects_YES,
top10_creators_by_average_goal_NO,
top10_creators_by_average_goal_YES,
category_in_top_10_NO,
category_in_top_10_YES,
fem_creators_greater_than_male_creators_NO,
fem_creators_greater_than_male_creators_YES,
fem_projects_greater_than_male_projects_NO,
fem_projects_greater_than_male_projects_YES,
afinn_positive_higher_NO,
afinn_positive_higher_YES,
numerical_pred_ridge_blurb
  )
```


```{r Model Deployment, echo = FALSE}
base_data2_data_matrix <- as.matrix(sapply(base_data2, as.numeric))
test_pool <- catboost.load_pool(data = base_data2_data_matrix, label = NULL)
bst_pred <- catboost.predict(model, test_pool)
bst_classifications <- ifelse(bst_pred > 0.5, "YES", "NO")


write.table(bst_classifications, "success_group5.csv", row.names = FALSE)

# write.table(names(cleans),"test_features.csv",row.names = FALSE)
```

